---
title: 'Assignment #6 Arima'
author: "Aolong Zhang"
date: "2023-11-22"
output: html_document
---

```{r}
library(readxl)
Tesla_sales <- read_excel("C:/Users/17215/OneDrive/Desktop/Tesla sales.xlsx")
View(Tesla_sales)

class(Tesla_sales)

## convert dataset to time series
data = ts(Tesla_sales$`Total Sales`, start = c(2015),end = c(2023,6),
           frequency = 12)

library(fpp)
library(fpp2)

plot(data)

## choose the time window
data1 <- window(data, start = c(2022,4))
plot(data1)

## acf
Acf(data1)

## test if data is stationary, it shows no stationary
adf.test(data1)

## we need 1 difference to do it, and there is no seasonality
nsdiffs(data1)
ndiffs(data1)

#tsdisplay plots ACF,PACF and timeseries plot together
tsdisplay(data1)

## auto.arima gives the best model
auto.arima(data1, trace = TRUE)
fit3 <- Arima(data1, order=c(0,1,0))

# See the output of ARIMA
fit3

# Store the residuals
res <- residuals(fit3)


## residual analysis

tsdisplay(res)
Acf(fit3$residuals)
plot.ts(residuals(fit3))
hist(fit3$residuals)


## forecast and plot

fcast = forecast(fit3, h=5)           
plot(fcast)          
plot(data1)
lines(fcast$fitted,col = "red")


```

# Explain the output  
The model selected is ARIMA(0,1,0), which indicates that it is a simple differencing model without any autoregressive (AR) or moving average (MA) terms.p=0 means No AR terms are included, meaning past values of the series are not used to predict future values.d=1 means the series is differenced once to make it stationary, and q=0 means no moving averge  terms are included.


# Run Residual Analysis  
1. The plot shows residuals fluctuating over time with no obvious trend or seasonality in the residuals.  

2. he ACF plot for residuals shows that all the autocorrelations are within the confidence bounds, which is good.  

3. The PACF plot also shows that partial autocorrelations are within the confidence bounds for the first few lags.  

4. It is not a  normal distribution; it shows a potential right skewness.  


```{r}
tsdisplay(res)
Acf(fit3$residuals)
plot.ts(residuals(fit3))
hist(fit3$residuals)


```

# Perform and Plot forecast for the next 5 periods  

```{r}
fcast = forecast(fit3, h=5)           
plot(fcast)          
plot(data1)
lines(fcast$fitted,col = "red")

```

# Show the accuracy of Arima model  

MAE(mean absolute error) is 2902, which is actually better than all my previous models, which is good.
```{r}
accuracy(fcast)
```



